A Dataset of Scratch Programs:\\Scraped, Shaped and Scored

### 2017-02-19 MSR-Scratch.tex
Fixed error on remix stats

\begin{table}[]
	\centering
	\begin{tabular}{lrrrrrr}
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Projects per username&2.3&1&1&1&2&868\\
		Sprites \emph{pp}&5.3&0&1&2&5&525\\
		Scripts \emph{pp}&16.2&0&2&4&11&3,038\\
		Blocks \emph{pp}&144.3&0&9&26&69&34,622\\
		Custom block def. \emph{pp}&0.6&0&0&0&0&372\\
		Total views \emph{pp}&5.8&0&1&1&4&27,993\\
		Total remixes \emph{pp}&197.1&0&0&0&0&14,951K \\ %14,951,164  \\
		Total favorites \emph{pp}&0.5&0&0&0&0&2,582\\
		Dr.Scratch mastery \emph{pp}&8.9&0&6&8&11&21\\
		\hline
	\end{tabular}
	\caption{Summary statistics of the dataset (\emph{pp} stands for per project).}
	\label{tbl-stats}
\end{table}

>>>>

\begin{table}[]
	\centering
	\begin{tabular}{lrrrrrr}
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Projects per username&2.3&1&1&1&2&868\\
		Sprites \emph{pp}&5.3&0&1&2&5&525\\
		Scripts \emph{pp}&16.2&0&2&4&11&3,038\\
		Blocks \emph{pp}&144.3&0&9&26&69&34,622\\
		Custom block def. \emph{pp}&0.6&0&0&0&0&372\\
		Total views \emph{pp}&5.8&0&1&1&4&27,993\\
		Total remixes \emph{pp}&0.1&0&0&0&0&306\\
		Total favorites \emph{pp}&0.5&0&0&0&0&2,582\\
		Dr.Scratch mastery \emph{pp}&8.9&0&6&8&11&21\\
		\hline
	\end{tabular}
	\caption{Summary statistics of the dataset (\emph{pp} stands for per project).}
	\label{tbl-stats}
\end{table}
